Unity in diversity: Children from 17 diverse communities process gaze in similar ways

### 2024-03-14 analysis/gafo-cc-visuals.Rmd

```{r}
library(tidyverse)
library(ggpubr)
library(ggthemes)
library(tidyboot)
library(maps)
library(brms)
library(cowplot)
library(png)
library(ggimage)
library(ggridges)
```

@@

>>>>

```{r}
library(tidyverse)
library(ggpubr)
library(ggthemes)
library(tidyboot)
library(maps)
library(brms)
library(cowplot)
library(png)
library(ggimage)
library(ggridges)
library(ggside)
```

@@

# talk plots

```{r}
meand <- ddata%>%
  filter(community %in% c("Leipzig (Germany)", "Akure (Nigeria)", "Malatya (Turkey)"))%>%
  group_by(community)%>%
  tidyboot_mean(col = mean_click)

ggplot()+
  #geom_point(data = ddata%>%filter(community %in% c("Akure (Nigeria)")), aes(x = ageinyears+ min(data$ageinyears), y = mean_click, col = community), alpha = 0.25)+
    geom_point(data = ddata%>%filter(community %in% c("Leipzig (Germany)", "Akure (Nigeria)", "Malatya (Turkey)")), aes(x = ageinyears+ min(data$ageinyears), y = mean_click, col = community), alpha = 0.25)+
  #geom_smooth(data = post%>%filter(community %in% c("Akure (Nigeria)")), aes(x = ageinyears, y = Estimate, ymin = Q2.5, ymax = Q97.5, fill =community, col = community), stat = "identity", alpha = .25)+
    geom_smooth(data = post%>%filter(community %in% c("Leipzig (Germany)",  "Akure (Nigeria)", "Malatya (Turkey)")), aes(x = ageinyears, y = Estimate, ymin = Q2.5, ymax = Q97.5, fill =community, col = community), stat = "identity", alpha = .25)+
  #geom_ysidedensity(data = ddata%>%filter(community %in% c("Akure (Nigeria)")), aes(y = mean_click, fill = community),col = "white",alpha = 0.5)+
    #geom_ysidedensity(data = ddata%>%filter(community %in% c("Leipzig (Germany)",  "Akure (Nigeria)", "Malatya (Turkey)")), aes(y = mean_click, fill = community),col = "white",alpha = 0.5)+
  geom_ysidepoint(data = meand, aes(y =mean, col = community, x = community), pch = 4, orientation = "x", size = 2, stroke = 2)+
  geom_ysidesegment(data = meand, aes(y =ci_lower, yend = ci_upper , col = community, x = community, xend = community), size = 1)+
  theme_classic()+
    scale_x_continuous(limits = c(2,9))+
  scale_y_continuous(limits = c(0,1000))+
  scale_fill_colorblind(name = "Community", guide = "none")+
  scale_color_colorblind(name = "Community", guide = "none")+
  labs(x = "Age", y="Cognitive measure (Imprecision)")+
  theme(legend.position = "right")+
  theme(#panel.border = element_rect(color = "black",fill = NA,size = .25),
        ggside.panel.border = element_blank(),
        ggside.panel.scale.y = .25,
        #axis.title.x = element_text(hjust = 0.2),
        legend.position = c(0.85,0.3),
        legend.background = element_blank())+
  theme_ggside_void()
```

```{r}
ggsave("../../../../../../Desktop/dev4.png", width = 10, height = 6, scale = 1)
```

### 2024-03-14 paper/paper.tex

We conducted a large-scale cross-cultural study on the development of gaze-following abilities to study potentially universal processing signatures and their development. Previous developmental studies focused on the onset of gaze following in infancy (\emph{15}, \emph{16}). The 1311 participants in the study lived in 17 different communities spread over five continents (Fig. \ref{fig:fig1}A, Tab. \ref{tab:tab1}). The countries from which data was contributed to the study represented 46 \% of the world's population. Communities covered a broad spectrum of geographical locations, social and political systems, languages, and subsistence styles (see Supplemental Materials).

@@

\caption{(A) Data collection sites. Points show approximate geographical location of the data collection sites, coloring shows the sample sizes. (B) Screenshot from the task. The scene depicts the choice phase in a test trial. Participants had to use the gaze of the agent to locate the balloon and click on the hedge where they thought the balloon was. Agents, audio recordings and backgrounds were adpated to each cultural setting. (C) Graphical illustration of the cognitive model. Individuals infer the target of an agent's attention by estimating a vector based on the position of the pupils within the eyes. This process is noisy, illustrated by the different vectors. Individuals differ in their level of precision (indicated by alpha). Regardless of the level of precision, the further out the target lands, the less precise the model predicts individuals to be.}\label{fig:fig1}
\end{figure}

@@

\caption{\label{tab:tab1}Participant demographics.}
\centering
\resizebox{\linewidth}{!}{
\begin{tabular}[t]{llllllll}
\toprule
Continent & Country & Community & N(male) & Age (range) & Language & Market integration & Touchscreen\\
\midrule
America & Argentina & Buenos Aires & 105 (53) & 4.72 (3.00 - 6.96) & Spanish (Rioplatense) & high & 0.90\\
 & Mexico & Ocuilan & 125 (61) & 4.97 (2.57 - 6.95) & Spanish (Mexican) & medium & 0.77\\
 & USA & Stanford & 100 (56) & 5.00 (2.52 - 7.90) & English (American) & high & 0.98\\
Africa & Namibia & Hai||om & 60 (38) & 5.85 (2.74 - 8.34) & Hai||om & low & 0.05\\
 &  & Khwe & 59 (24) & 5.84 (3.38 - 8.63) & Khwedam & low & 0.19\\
\addlinespace
 &  & Windhoek & 41 (18) & 5.68 (2.66 - 8.66) & English (Nigerian) & high & 0.95\\
 & Nigeria & Akure & 114 (53) & 5.07 (2.57 - 7.33) & English (Nigerian) & high & 0.91\\
 & Rep. Congo & BaYaka & 28 (12) & 7.86 (3.94 - 10.56) & BaYaka & low & 0.00\\
 &  & Bandongo & 30 (11) & 7.45 (3.50 - 10.95) & Lingala & low & 0.00\\
 & Sambia & Chimfunshi & 22 (5) & 5.98 (2.88 - 8.00) & Bemba & medium & 0.14\\
\addlinespace
 & Uganda & Nyabyeya & 51 (27) & 5.41 (3.27 - 8.21) & Swahili & medium & 0.49\\
Europe & Germany & Leipzig & 100 (48) & 4.88 (2.53 - 6.95) & German & high & 0.89\\
 & UK & Plymouth & 70 (30) & 6.02 (2.38 - 8.94) & English (British) & high & 0.99\\
Asia & China & Beijing & 123 (62) & 5.47 (2.69 - 8.48) & Mandarin & high & 0.95\\
 & India & Pune & 155 (75) & 6.14 (3.06 - 8.83) & English (Indian) / Marathi & high & 0.92\\
\addlinespace
 & Turkey & Malatya & 85 (40) & 5.02 (2.75 - 7.12) & Turkish & high & 1.00\\
Oceania & New Zealand & Auckland & 43 (19) & 5.14 (2.81 - 8.75) & English (New Zealand) & high & 0.95\\
\bottomrule
\end{tabular}}
\end{table}

@@

As the first step, we investigated developmental gains. Across all 17 communities, we found a substantial increase in average levels of precision with age (fixed effect: \(\beta\) = -0.30, 95\% HDI (-0.39 - -0.21); range of community-level effects: \(\beta_{min}\) = -0.06, 95\% HDI (-0.17 - 0.06) to \(\beta_{max}\) = -0.58, 95\% HDI (-0.69 - -0.46). There were marked differences between communities: highly market-integrated communities around the globe showed higher levels of precision compared to less market-integrated communities. However, we believe that these results are better explained by exposure to technology than market integration. We discuss them in more detail below. Differences between communities were small compared to differences between individuals: communities did not form homogeneous clusters but largely overlapping distributions in that some individuals from communities with a lower average level of precision performed better compared to some individuals from a setting with a very high average level of precision. Furthermore, in all communities, some 4-year-olds outperformed children two years older than them (see Fig. \ref{fig:fig2}A).

@@

Consistent developmental gains alone cannot inform us about the cognitive processes children use when locating the agent's focus of attention. Recent computational work modeled gaze following as social vector estimation (\emph{18}). When observing the eyes, onlookers estimate a vector from the center of the eye through the pupil. The focus of attention is the location wherever the estimated vectors from both eyes hit a surface (Fig. \ref{fig:fig1}C). The estimation process is not perfect, but each individual has a systematic level of uncertainty, which is conceptualized as the cause of individual differences. Importantly, this process model predicts a clear performance signature in our cross-cultural gaze following task: Trials in which the agent looks further away from the center (i.e.~to the left or right side of the screen) should result in lower levels of precision, compared to trials in which the agent looks closer to the middle. This prediction is best understood by considering a similar phenomenon: pointing a torch light to a flat surface. The width of the light beam represents each individual's level of uncertainty in vector estimation. When the torch is directed straight down, the light beam is concentrated in a relatively small area. When the torch is rotated to the side, the light from one half of the cone must travel further than the light from the other half to reach the surface. As a consequence, the light is spread over a wider area.

The processing signature was clearly visible across all 17 communities. Precision decreased when the agent looked at locations further away from the center (fixed effect: \(\beta\) = 0.48, 95\% HDI ( - 0.54); range of community-level effects: \(\beta_{min}\) = 0.58, 95\% HDI (0.51 - 0.66) to \(\beta_{max}\) = 0.22, 95\% HDI (0.05 - 0.38). Visualization of the data showed the predicted u-shaped pattern in all communities (see Fig. \ref{fig:fig2}B). These results indicate a universal cognitive process used by children in all communities. There is, however, an alternative way in which the u = shaped pattern might arise: it would also arise when participants ignored the agent's gaze and instead always selected the middle of the screen (center bias). To rule out this alternative explanation, we directly compared three cognitive models that made different assumptions about how participants' responses were generated: the focal vector-based gaze estimation model described above, a center-bias model where participants always select the center, and a random guessing model where participants select random locations. For every community, we found overwhelming support for the gaze estimation model (min \(BF_{10}\) \textless{} 1000 for comparisons with both alternative models). Taken together, children from all 17 communities processed gaze in similar ways.

What is left to explain are the marked community- and individual-level differences. In addition to the gaze-following task, caregivers filled out a small questionnaire about children's access to screen-based technology and the composition of their households. On an individual level, we found that across communities, children with access to touchscreen devices had higher levels of precision (\(\beta\) = -0.14, SE = 0.04, 95\% CrI = -0.22 - -0.07). On a community level, we also saw that average performance was lowest in the communities in which touchscreen devices were the least frequent (Fig. \ref{fig:fig3}). Thus, methodological factors likely explained the marked differences between communities.

@@

On an individual level, other factors likely generated individual differences because there was substantial variation even in communities where almost all children had access to touchscreens. Previous work suggested that social cognition develops in social interaction (\emph{19}--\emph{21}), in particular, with older siblings (\emph{22}, \emph{23}). We found tentative support for this idea in the form of a small but consistent effect in the direction that participants living together with more children older than themselves had slightly higher levels of precision (\(\beta\) = -0.01, SE = 0.01, 95\% CrI = -0.04 - 0.01).

Following and understanding gaze is a foundational building block of human social cognition (\emph{8}, \emph{9}). A substantial body of work has explored the developmental onset of gaze following in a few selected cultural settings (\emph{10}--\emph{12}, \emph{15}, \emph{16}). The data reported here provides evidence that children all over the world process gaze in the same way. Key performance signatures of a model that sees gaze following as a form of social vector estimation were found in the data of all 17 distinct cultural communities. The cognitive processes underlying gaze following are thus likely to be rooted in humans' evolved cognitive architecture, which is -- presumably -- later refined during social interaction. The phylogenetic roots of these processes might possibly lie much deeper as primates from a wide range of species follow gaze (\emph{24}--\emph{26}). Yet, if they also show the same processing signatures has yet to be explored.

There are important limitations to this study. The methodological factors that influenced performance might have overshadowed individual and community-level differences that originate from other sources. Importantly, this does not affect our interpretation of the data as evidence for shared cognitive processing because the key processing signatures were present in all communities. The role that social interaction plays as a potential driver of development and source of individual differences is vastly under-explored in the current study. The small effect of the exposure to older children does not indicate which aspects of social interaction enhance gaze processing. Naturalistic data directly recording social interactions across communities would offer crucial information to close this explanatory gap. Recent work in the field of language acquisition has shown how technological innovations can be used to close this explanatory gap.

@@

\leavevmode\vadjust pre{\hypertarget{ref-prein2023variation}{}}%
\CSLLeftMargin{18. }%
\CSLRightInline{J. C. Prein, L. Maurits, A. Werwach, D. B. M. Haun, M. Bohn, Variation in gaze understanding across the life span: {A} process-level perspective. \emph{{PsyArXiv}}, doi: \href{https://doi.org/10.31234/osf.io/dy73a}{10.31234/osf.io/dy73a} (2023).}

\leavevmode\vadjust pre{\hypertarget{ref-barresi1996intentional}{}}%
\CSLLeftMargin{19. }%
\CSLRightInline{J. Barresi, C. Moore, Intentional relations and social understanding. \emph{Behavioral and brain sciences} \textbf{19}, 107--122 (1996).}

\leavevmode\vadjust pre{\hypertarget{ref-perner1994theory}{}}%
\CSLLeftMargin{20. }%
\CSLRightInline{J. Perner, T. Ruffman, S. R. Leekam, Theory of mind is contagious: You catch it from your sibs. \emph{Child Development} \textbf{65}, 1228--1238 (1994).}

\leavevmode\vadjust pre{\hypertarget{ref-rakoczy2022foundations}{}}%
\CSLLeftMargin{21. }%
\CSLRightInline{H. Rakoczy, Foundations of theory of mind and its development in early childhood. \emph{Nature Reviews Psychology} \textbf{1}, 223--235 (2022).}

\leavevmode\vadjust pre{\hypertarget{ref-lewis1996social}{}}%
\CSLLeftMargin{22. }%
\CSLRightInline{C. Lewis, N. H. Freeman, C. Kyriakidou, K. Maridaki-Kassotaki, D. M. Berridge, Social influences on false belief access: Specific sibling influences or general apprenticeship? \emph{Child development} \textbf{67}, 2930--2947 (1996).}

\leavevmode\vadjust pre{\hypertarget{ref-ruffman1998older}{}}%
\CSLLeftMargin{23. }%
\CSLRightInline{T. Ruffman, J. Perner, M. Naito, L. Parkin, W. A. Clements, Older (but not younger) siblings facilitate false belief understanding. \emph{Developmental psychology} \textbf{34}, 161 (1998).}

\leavevmode\vadjust pre{\hypertarget{ref-rosati2009looking}{}}%
\CSLLeftMargin{24. }%
\CSLRightInline{A. G. Rosati, B. Hare, Looking past the model species: Diversity in gaze-following skills across primates. \emph{Current opinion in neurobiology} \textbf{19}, 45--51 (2009).}

\leavevmode\vadjust pre{\hypertarget{ref-tomasello1998five}{}}%
\CSLLeftMargin{25. }%
\CSLRightInline{M. Tomasello, J. Call, B. Hare, Five primate species follow the visual gaze of conspecifics. \emph{Animal behaviour} \textbf{55}, 1063--1069 (1998).}

\leavevmode\vadjust pre{\hypertarget{ref-itakura2004gaze}{}}%
\CSLLeftMargin{26. }%
\CSLRightInline{S. Itakura, Gaze-following and joint visual attention in nonhuman animals, \emph{Japanese Psychological Research}. \textbf{46} (2004)pp. 216--226.}

>>>>

We conducted a large-scale cross-cultural study on the development of gaze-following abilities to study potentially universal processing signatures and their development. Previous developmental studies focused on the onset of gaze following in infancy (\emph{15}, \emph{16}). The 1377 participants in the study lived in 17 different communities spread over five continents (Fig. \ref{fig:fig1}A, Tab. \ref{tab:tab1}). The countries from which data was contributed to the study represented 46 \% of the world's population. Communities covered a broad spectrum of geographical locations, social and political systems, languages, and subsistence styles (see Supplemental Materials).

@@

\caption{(A) Data collection sites. Points show approximate geographical location of the data collection sites, coloring shows the sample sizes. (B) Screenshot from the task. The scene depicts the choice phase in a test trial. Participants had to use the gaze of the agent to locate the balloon and click on the hedge where they thought the balloon was. Agents, audio recordings and backgrounds were adpated to each cultural setting. (C) Drawings used as agents across cultural settings. (D) Graphical illustration of the cognitive model. Individuals infer the target of an agent's attention by estimating a vector based on the position of the pupils within the eyes. This process is noisy, illustrated by the different vectors. Individuals differ in their level of precision (indicated by alpha). For a given level of precision, the further out the target lands, the less precise the model predicts individuals to be. Solid and transparent dots show simualted means and individual data points to illustrate the predicted effect of target position.}\label{fig:fig1}
\end{figure}

@@

\caption{\label{tab:tab1}Participant demographics.}
\centering
\resizebox{\linewidth}{!}{
\begin{tabular}[t]{llllllll}
\toprule
Continent & Country & Community & N(male) & Age (range) & Language & Market integration & Touchscreen\\
\midrule
America & Argentina & Buenos Aires & 105 (53) & 4.72 (3.00 - 6.96) & Spanish (Rioplatense) & high & 0.90\\
 & Mexico & Ocuilan & 127 (63) & 4.96 (2.57 - 6.95) & Spanish (Mexican) & medium & 0.77\\
 & USA & Stanford & 98 (54) & 4.99 (2.52 - 7.90) & English (American) & high & 0.98\\
Africa & Namibia & Hai||om & 60 (38) & 5.85 (2.74 - 8.34) & Hai||om & low & 0.05\\
 &  & Khwe & 59 (24) & 5.84 (3.38 - 8.63) & Khwedam & low & 0.19\\
\addlinespace
 &  & Windhoek & 39 (17) & 5.69 (2.66 - 8.66) & English (Nigerian) & high & 0.95\\
 & Nigeria & Akure & 114 (54) & 5.07 (2.57 - 7.33) & English (Nigerian) & high & 0.91\\
 & Rep. Congo & BaYaka & 29 (13) & 7.80 (3.94 - 10.56) & BaYaka & low & 0.00\\
 &  & Bandongo & 30 (11) & 7.45 (3.50 - 10.95) & Lingala & low & 0.00\\
 & Uganda & Nyabyeya & 125 (62) & 5.94 (2.67 - 8.92) & Bemba & medium & 0.34\\
\addlinespace
 & Zambia & Chimfunshi & 22 (5) & 5.98 (2.88 - 8.00) & Swahili & medium & 0.14\\
Europe & Germany & Leipzig & 100 (48) & 4.88 (2.53 - 6.95) & German & high & 0.89\\
 & UK & Plymouth & 70 (30) & 6.02 (2.38 - 8.94) & English (British) & high & 0.99\\
Asia & China & Beijing & 123 (62) & 5.47 (2.69 - 8.48) & Mandarin & high & 0.95\\
 & India & Pune & 148 (73) & 6.14 (3.06 - 8.83) & English (Indian) / Marathi & high & 0.93\\
\addlinespace
 & Türkiye & Malatya & 85 (40) & 5.02 (2.75 - 7.12) & Turkish & high & 1.00\\
Oceania & New Zealand & Auckland & 43 (19) & 5.14 (2.81 - 8.75) & English (New Zealand) & high & 0.95\\
\bottomrule
\end{tabular}}
\end{table}

@@

As the first step, we investigated developmental gains. Across all 17 communities, we found a substantial increase in average levels of precision with age (fixed effect in Bayesian regression model (\emph{18}): \(\beta\) = -0.30, 95\% HDI (-0.40 - -0.21); range of community-level effects in model: \(\beta_{min}\) = -0.06, 95\% HDI (-0.17 - 0.06) to \(\beta_{max}\) = -0.59, 95\% HDI (-0.70 - -0.47). Nevertheless, there were also marked differences between communities (see Fig. \ref{fig:fig2}A). In a cross-validation procedure, in which we trained a regression model on a subset of the data (training data) to later predict the held out data (testing data) (\emph{19}), we found that a model that assumed cross-cultural variation to outperform simple models in 100\% of cases (see Supplemental Material). At first glance, it seems that highly market-integrated communities around the globe showed higher levels of precision compared to less market-integrated communities (see Tab. \ref{tab:tab1}). However, believe that these results are better understood in terms of exposure to technology and we discuss them in more detail below. Furthermore, average differences between communities were small compared to differences between individuals: communities did not form homogeneous clusters but largely overlapping distributions in that some individuals from communities with a lower average level of precision performed better compared to some individuals from a setting with a very high average level of precision. Similarly, in all communities, some 4-year-olds outperformed children two years older than them (see Fig. \ref{fig:fig2}A).

@@

Consistent developmental gains alone cannot inform us about the cognitive processes children use when locating the agent's focus of attention. Recent computational work modeled gaze following as social vector estimation (\emph{20}). When observing the eyes, onlookers estimate a vector from the center of the eye through the pupil. The focus of attention is the location wherever the estimated vectors from both eyes hit a surface (Fig. \ref{fig:fig1}C). The estimation process is not perfect, but each individual has a systematic level of uncertainty, which is conceptualized as the cause of individual differences. Importantly, this process model predicts a clear performance signature in our cross-cultural gaze following task: Trials in which the agent looks further away from the center (i.e.~to the left or right side of the screen) should result in lower levels of precision, compared to trials in which the agent looks closer to the middle. This prediction is best understood by considering a similar phenomenon: pointing a torch light to a flat surface. The width of the light beam represents each individual's level of uncertainty in vector estimation. When the torch is directed straight down, the light beam is concentrated in a relatively small area. When the torch is rotated to the side, the light from one half of the cone must travel further than the light from the other half to reach the surface. As a consequence, the light is spread over a wider area.

The processing signature was clearly visible across all 17 communities. Precision decreased when the agent looked at locations further away from the center (fixed effect: \(\beta\) = 0.47, 95\% HDI ( - 0.54); range of community-level effects: \(\beta_{min}\) = 0.58, 95\% HDI (0.51 - 0.66) to \(\beta_{max}\) = 0.16, 95\% HDI (-0.01 - 0.34). Visualization of the data showed the predicted u-shaped pattern in all communities (see Fig. \ref{fig:fig2}B). These results indicate a universal cognitive process used by children in all communities. There is, however, an alternative way in which the u = shaped pattern might arise: it would also arise when participants ignored the agent's gaze and instead always selected the middle of the screen (center bias). To rule out this alternative explanation, we directly compared three cognitive models that made different assumptions about how participants' responses were generated: the focal vector-based gaze estimation model described above, a center-bias model where participants always select the center, and a random guessing model where participants select random locations. For every community, we found overwhelming support for the gaze estimation model (min \(BF_{10}\) \textgreater{} 1000 for comparisons with both alternative models). Taken together, children from all 17 communities processed gaze in similar ways.

What is left to explain are the marked community- and individual-level differences. In addition to the gaze-following task, caregivers filled out a small questionnaire about children's access to screen-based technology and the composition of their households. On an individual level, we found that across communities, children with access to touchscreen devices had higher levels of precision (\(\beta\) = , SE = , 95\% CrI = - ). On a community level, we also saw that average performance was lowest in the communities in which touchscreen devices were the least frequent (Fig. \ref{fig:fig3}). Thus, methodological factors likely explained the marked differences between communities.

@@

Based on this, we also computed the number of older children living in the household. We did not pre-register this, but decided to also include this variable because prior work on advanced forms of social cognition has suggested that the presence of older siblings is slightly more predictive of development compared to other aspects of household composition (e.g., \emph{21}, \emph{22}, but see \emph{23}). We think that gaze following improves though practice during social interaction. Particularly supportive, we believe, are situations in which it is difficult to infer the goals and intentions of another person based on other information sources (e.g., language or context). In such situations, children have to pay closer attention to the interaction partner and use their gaze to make such inferences. We are well aware that the numbers in the questionnaire are very far removed from these forms of social interaction. Thus, at best, they are a very coarse approximation. As a consequence, we do not expect there to be a very strong link between the two. We sincerely hope that future work will be able to directly assess children's social interactions.

On an individual level, other factors likely generated individual differences because there was substantial variation even in communities where almost all children had access to touchscreens. Previous work suggested that social cognition develops in social interaction (\emph{24}--\emph{26}), in particular, with older siblings (\emph{21}, \emph{22}). We found tentative support for this idea in the form of a small but consistent effect in the direction that participants living together with more children older than themselves (relative to other children from the same setting) had slightly higher levels of precision (\(\beta\) = , SE = , 95\% CrI = - ).

Following and understanding gaze is a foundational building block of human social cognition (\emph{8}, \emph{9}). A substantial body of work has explored the developmental onset of gaze following in a few selected cultural settings (\emph{10}--\emph{12}, \emph{15}, \emph{16}, \emph{27}). The data reported here provides evidence that children all over the world process gaze in the same way. Key performance signatures of a model that sees gaze following as a form of social vector estimation were found in the data of all 17 distinct cultural communities. The cognitive processes underlying gaze following are thus likely to be rooted in humans' evolved cognitive architecture, which is -- presumably -- later refined during social interaction (\emph{28}--\emph{30}). The phylogenetic roots of these processes might possibly lie much deeper as primates from a wide range of species follow gaze (\emph{31}--\emph{34}). Yet, if they also show the same processing signatures has yet to be explored.

There are important limitations to this study. The methodological factors that influenced performance might have overshadowed individual and community-level differences that originate from other sources. Importantly, this does not affect our interpretation of the data as evidence for shared cognitive processing because the key processing signatures were present in all communities. The role that social interaction plays as a potential driver of development and source of individual differences is vastly under-explored in the current study. The small effect of the exposure to older children does not indicate which aspects of social interaction enhance gaze processing. Naturalistic data directly recording social interactions across communities would offer crucial information to close this explanatory gap. Recent work in the field of language acquisition has shown how technological innovations can be used to close this explanatory gap (\emph{35}, \emph{36}).

@@

\leavevmode\vadjust pre{\hypertarget{ref-burkner2019bayesian}{}}%
\CSLLeftMargin{18. }%
\CSLRightInline{P.-C. Bürkner, Bayesian item response modeling in r with brms and stan. \emph{arXiv preprint arXiv:1905.09501} (2019).}

\leavevmode\vadjust pre{\hypertarget{ref-stengelin2023children}{}}%
\CSLLeftMargin{19. }%
\CSLRightInline{R. Stengelin, R. Ball, L. Maurits, P. Kanngiesser, D. B. Haun, Children over-imitate adults and peers more than puppets. \emph{Developmental Science} \textbf{26}, e13303 (2023).}

\leavevmode\vadjust pre{\hypertarget{ref-prein2023variation}{}}%
\CSLLeftMargin{20. }%
\CSLRightInline{J. C. Prein, L. Maurits, A. Werwach, D. B. M. Haun, M. Bohn, Variation in gaze understanding across the life span: {A} process-level perspective. \emph{{PsyArXiv}}, doi: \href{https://doi.org/10.31234/osf.io/dy73a}{10.31234/osf.io/dy73a} (2023).}

\leavevmode\vadjust pre{\hypertarget{ref-lewis1996social}{}}%
\CSLLeftMargin{21. }%
\CSLRightInline{C. Lewis, N. H. Freeman, C. Kyriakidou, K. Maridaki-Kassotaki, D. M. Berridge, Social influences on false belief access: Specific sibling influences or general apprenticeship? \emph{Child development} \textbf{67}, 2930--2947 (1996).}

\leavevmode\vadjust pre{\hypertarget{ref-ruffman1998older}{}}%
\CSLLeftMargin{22. }%
\CSLRightInline{T. Ruffman, J. Perner, M. Naito, L. Parkin, W. A. Clements, Older (but not younger) siblings facilitate false belief understanding. \emph{Developmental psychology} \textbf{34}, 161 (1998).}

\leavevmode\vadjust pre{\hypertarget{ref-peterson2003opening}{}}%
\CSLLeftMargin{23. }%
\CSLRightInline{C. Peterson, V. Slaughter, Opening windows into the mind: Mothers' preferences for mental state explanations and children's theory of mind. \emph{Cognitive Development} \textbf{18}, 399--429 (2003).}

\leavevmode\vadjust pre{\hypertarget{ref-barresi1996intentional}{}}%
\CSLLeftMargin{24. }%
\CSLRightInline{J. Barresi, C. Moore, Intentional relations and social understanding. \emph{Behavioral and brain sciences} \textbf{19}, 107--122 (1996).}

\leavevmode\vadjust pre{\hypertarget{ref-perner1994theory}{}}%
\CSLLeftMargin{25. }%
\CSLRightInline{J. Perner, T. Ruffman, S. R. Leekam, Theory of mind is contagious: You catch it from your sibs. \emph{Child Development} \textbf{65}, 1228--1238 (1994).}

\leavevmode\vadjust pre{\hypertarget{ref-rakoczy2022foundations}{}}%
\CSLLeftMargin{26. }%
\CSLRightInline{H. Rakoczy, Foundations of theory of mind and its development in early childhood. \emph{Nature Reviews Psychology} \textbf{1}, 223--235 (2022).}

\leavevmode\vadjust pre{\hypertarget{ref-moore2008development}{}}%
\CSLLeftMargin{27. }%
\CSLRightInline{C. Moore, The development of gaze following. \emph{Child Development Perspectives} \textbf{2}, 66--70 (2008).}

\leavevmode\vadjust pre{\hypertarget{ref-astor2020social}{}}%
\CSLLeftMargin{28. }%
\CSLRightInline{K. Astor, M. Lindskog, L. Forssman, B. Kenward, M. Fransson, A. Skalkidou, A. Tharner, J. Cassé, G. Gredebäck, Social and emotional contexts predict the development of gaze following in early infancy. \emph{Royal Society open science} \textbf{7}, 201178 (2020).}

\leavevmode\vadjust pre{\hypertarget{ref-movellan2002development}{}}%
\CSLLeftMargin{29. }%
\CSLRightInline{J. R. Movellan, J. S. Watson, {``The development of gaze following as a bayesian systems identification problem''} in \emph{Proceedings 2nd International Conference on Development and Learning. ICDL 2002} (IEEE, 2002), pp. 34--40.}

\leavevmode\vadjust pre{\hypertarget{ref-senju2015early}{}}%
\CSLLeftMargin{30. }%
\CSLRightInline{A. Senju, A. Vernetti, N. Ganea, K. Hudry, L. Tucker, T. Charman, M. H. Johnson, Early social experience affects the development of eye gaze processing. \emph{Current Biology} \textbf{25}, 3086--3091 (2015).}

\leavevmode\vadjust pre{\hypertarget{ref-rosati2009looking}{}}%
\CSLLeftMargin{31. }%
\CSLRightInline{A. G. Rosati, B. Hare, Looking past the model species: Diversity in gaze-following skills across primates. \emph{Current opinion in neurobiology} \textbf{19}, 45--51 (2009).}

\leavevmode\vadjust pre{\hypertarget{ref-tomasello1998five}{}}%
\CSLLeftMargin{32. }%
\CSLRightInline{M. Tomasello, J. Call, B. Hare, Five primate species follow the visual gaze of conspecifics. \emph{Animal behaviour} \textbf{55}, 1063--1069 (1998).}

\leavevmode\vadjust pre{\hypertarget{ref-itakura2004gaze}{}}%
\CSLLeftMargin{33. }%
\CSLRightInline{S. Itakura, Gaze-following and joint visual attention in nonhuman animals, \emph{Japanese Psychological Research}. \textbf{46} (2004)pp. 216--226.}

\leavevmode\vadjust pre{\hypertarget{ref-kano2014cross}{}}%
\CSLLeftMargin{34. }%
\CSLRightInline{F. Kano, J. Call, Cross-species variation in gaze following and conspecific preference among great apes, human infants and adults. \emph{Animal Behaviour} \textbf{91}, 137--150 (2014).}

\leavevmode\vadjust pre{\hypertarget{ref-bergelson2023everyday}{}}%
\CSLLeftMargin{35. }%
\CSLRightInline{E. Bergelson, M. Soderstrom, I.-C. Schwarz, C. F. Rowland, N. Ramirez-Esparza, L. R. Hamrick, E. Marklund, M. Kalashnikova, A. Guez, M. Casillas, others, Everyday language input and production in 1,001 children from six continents. \emph{Proceedings of the National Academy of Sciences} \textbf{120}, e2300671120 (2023).}

\leavevmode\vadjust pre{\hypertarget{ref-donnelly2021longitudinal}{}}%
\CSLLeftMargin{36. }%
\CSLRightInline{S. Donnelly, E. Kidd, The longitudinal relationship between conversational turn-taking and vocabulary growth in early language development. \emph{Child Development} \textbf{92}, 609--625 (2021).}
